Something with Networking

### 2024-12-29 talk/include/slides.tex
Update and complete slides.tex

\section{Topics}
\subsection{Entropy}
\begin{frame}
    % \frametitle{Entropy}
    The entropy can be calculated as $H = -\sum_{i=1}^{n} p_i \log_2(p_i)$. It represents how disordered a message is. Highly encrypted messages are near to random data.
    It is also practical to consider the variation of entropy in the clock domain.
    \begin{table}[h]
    \centering
    \caption{Average entropy for common protocols}
    \resizebox{\columnwidth}{!}{
        \begin{tabular}{|l|lllll|}
        \hline
        \multirow{2}{*}{} & \multicolumn{5}{c|}{Protocol Name}                                                                                                   \\ \cline{2-6} 
                          & \multicolumn{1}{l|}{Shadowsocks} & \multicolumn{1}{l|}{HTTPS} & \multicolumn{1}{l|}{NaiveProxy} & \multicolumn{1}{l|}{Trojan} & Obfs4 \\ \hline
        Entropy          & \multicolumn{1}{l|}{7.999}      & \multicolumn{1}{l|}{7.977} & \multicolumn{1}{l|}{7.992}      & \multicolumn{1}{l|}{7.858}  & 7.999 \\ \hline
        \end{tabular}%
    }
    \end{table}
\end{frame}

@@

>>>>

\section{Detect, filter and categorize traffics}
\begin{frame}
    Passive detection analyzes the packets with a combination of multiple factors, such as \textbf{entropy}, \textbf{packet length}, and \textbf{TLS fingerpeints} (If TLS is used).
    A connection can also be considered and analyzed in the clock domain.

    Active detection furthermore requires the censors to intercept, tamper, and manipulate (mostly replay) packets. Such as sending probes (replaying modified or unmodified previous packets) and trying to implement famous \textbf{Man in the middle attack}.
\end{frame}

\subsection{Entropy}
\begin{frame}
    % \frametitle{Entropy}
    The entropy can be calculated as $H = -\sum_{i=1}^{n} p_i \log_2(p_i)$. It represents how disordered a message is. Highly encrypted messages are near to random data.
    It is also practical to consider the variation of entropy in the clock domain.
    \begin{table}[h]
    \centering
    \caption{Average entropy for common protocols}
    \resizebox{\columnwidth}{!}{
        \begin{tabular}{|l|lllll|}
        \hline
        \multirow{2}{*}{} & \multicolumn{5}{c|}{Protocol Name}                                                                                                   \\ \cline{2-6}
                          & \multicolumn{1}{l|}{Shadowsocks} & \multicolumn{1}{l|}{HTTPS} & \multicolumn{1}{l|}{NaiveProxy} & \multicolumn{1}{l|}{Trojan} & Obfs4 \\ \hline
        Entropy          & \multicolumn{1}{l|}{7.999}      & \multicolumn{1}{l|}{7.977} & \multicolumn{1}{l|}{7.992}      & \multicolumn{1}{l|}{7.858}  & 7.999 \\ \hline
        \end{tabular}%
    }
    \end{table}
\end{frame}

@@

\section{Block technologies}
\begin{frame}
    Generally, three ideas for blocking traffic are associated with the nature of network layers.
    \begin{enumerate}
        \item Drop packets, the layer 3 approach.
        \item Reset TCP connections, based on TCP connections' stateful nature.
        \item DNS pollution, raw DNS implementations without authentication and encryption will be vulnerable.
    \end{enumerate}
\end{frame}

\subsection{Factors for blocking designated connections}
\begin{frame}
    \begin{itemize}
        \item Using TCP/IP 5 tuple to specify a connection, as a system administrator does when they write an iptables statement. It is a layer 3 (the Network Layer) and layer 4 (the Transport Layer) based approach.
        \item Block a connection by SNI utilizes the nature of the HTTPS protocol stack, which lies on layer 7 (the Application Layer). It can also be mitigated with some experimental features such as ESNI and ECH.
    \end{itemize}
\end{frame}

\section{Circumvention technologies}
\begin{frame}
    As the title says, in the adversary between detection and circumvention, the opposite technologies are always associated with each other, which means they are always designed to combat each other.
    For passive detection, there are mitigations:
    \begin{itemize}
    \item Manipulating the bytes stream in order to combat \textbf{byte sequence analysis}.
    \item Insert padding bytes in the stream in order to combat \textbf{packet length analysis}.
    \item Alternating the order of sending packets in order to combat textbf{timing analysis}.
    \end{itemize}

    For active detection
    \begin{itemize}
    \item In order to mitigate \textbf{TLS fingerprinting}, Naiveproxy utilizes the network stack of chromium, which is open source and widely adopted.
    \item \textbf{Packet Length Analysis} can be combated by padding and dividing packets.
    \item  With the utilization of Chromium's network stack, Naiveproxy is supposed not to expose any outstanding \textbf{behaviors} that differ from standard behaviors of Chromium.
\end{itemize}
